Simulations

### 2020-12-10 Simulations.Rmd
Added box & whisker plot

nloop <- 1000
oldGap <- rep(NA, nloop)
newGap <- rep(NA, nloop)

for (i in 1:nloop) {
  season <- simulateSeason()
  points <- calcTotalPoints(season)
  oldEast <- returnOldEastern(points)
  oldWest <- returnOldWestern(points)
  newEast <- returnNewEastern(points)
  newWest <- returnNewWestern(points)
  oldGap[i] <- oldEast[8,2] - oldWest[8,2]
  newGap[i] <- newEast[8,2] - newWest[8,2]
}

@@

ggplot(df, aes(x = gap, fill = Rule_Type)) +
  geom_density(alpha = 0.4) +
  geom_vline(aes(xintercept = mean(oldGap)), col = 4) +
  geom_vline(data = dfDat, aes(xintercept = grp.mean, color = Rule_Type), linetype = "dashed") +
  xlab("Conference gap") +
  ylab("Density")

>>>>

nloop <- 1000
oldGap <- rep(NA, nloop)
newGap <- rep(NA, nloop)
seedPoints <- data.frame(integer())

for (i in 1:nloop) {
  season <- simulateSeason()
  points <- calcTotalPoints(season)
  oldEast <- returnOldEastern(points)
  oldWest <- returnOldWestern(points)
  newEast <- returnNewEastern(points)
  newWest <- returnNewWestern(points)
  oldGap[i] <- oldEast[8,2] - oldWest[8,2]
  newGap[i] <- newEast[8,2] - newWest[8,2]
  allTeams <- rbind(newEast, newWest)
  allTeams <- allTeams[order(-allTeams$totalPoints),]
  seeds <- data.frame(seedPlace = seq(1,30), points = allTeams$totalPoints)
  seedPoints <- rbind(seedPoints, seeds)
}

@@

ggplot(df, aes(x = gap, fill = Rule_Type)) +
  geom_density(alpha = 0.4) +
  geom_vline(data = dfDat, aes(xintercept = grp.mean, color = Rule_Type), linetype = "dashed") +
  xlab("Conference gap") +
  ylab("Density")

ggplot(seedPoints, aes(x = seedPlace, y = points, group = seedPlace)) +
  geom_boxplot() +
  coord_flip()
